---
title: "Lab 4: Single-Cell Analysis in R"
author: "Your Name"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Introduction

This RMarkdown document provides a template for single-cell analysis in R using Bioconductor packages.

## Load Libraries

```{r load-libraries}
library(tidyverse)
library(ggplot2)
library(SingleCellExperiment)
library(scater)
library(scran)
```

## Section 1: Data Loading

Replace this section with instructions for loading your single-cell data.

```{r load-data}
# Example: Load data
# sce <- read10X("path/to/data")
# Or use Bioconductor data packages
```

## Section 2: Quality Control

Perform initial quality control on the single-cell data.

```{r qc}
# QC metrics calculation would go here
# is.mito <- grepl("^MT-", rownames(sce))
# sce <- addPerCellQC(sce, subsets=list(Mito=is.mito))
```

## Section 3: Visualization

Create visualizations of your results.

```{r visualize}
# Visualization code would go here
# plotColData(sce, y="nCount_RNA")
```

## Session Info

```{r session-info}
sessionInfo()
```

